---
title: "Title"
author: "Author"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard)
library(jsonlite)
library(dplyr)
library(stringr)
library(purrr)
library(quantmod)
library(knitr)
library(DT)
library(highcharter)
library(dygraphs)
library(igraph)
library(visNetwork)
library(networkD3)

options(knitr.kable.NA = '')
```



Sidebar {.sidebar}
======================================================================= 

<br/>  

1. [Front Page](#front-page)

2. [Read Me](#read-me)

3. Table  
    3.1 [knitr](#knitr)   
    3.2 [DT](#dt)       

4. Plot  
    4.1 [highcharter](#highcharter)      
    4.2 [dygraphs](#dygraphs)     
    4.3 [visNetwork](#visnetwork)    
    4.4 [networkD3](#networkd3)    
    
5. [References](#references)


<br/>



Front Page {data-icon='fa-list'}
======================================================================= 

<br/>    
<br/>     
<br/>     
<br/>      
<br/>   

<center><font size="+8">Title</font></center>

<br/>  

<center><font size="+3">Author</font></center>
<center><font size="+3">Date</font></center>



Read Me {data-icon='fa-bookmark'}
======================================================================= 

<br/>    
<br/>     
<br/>

- <font size="+3">We use the following packages in this demo</font>
    - <font size="+2"><b>Set-up:</b> `flexdashboard`</font>
    - <font size="+2"><b>Data Preparation:</b> `jsonlite`, `dplyr`, `stringr`, `purrr`, `quantmod`</font>
    - <font size="+2"><b>Table:</b> `knitr`, `DT`</font>
    - <font size="+2"><b>Plot:</b> `highcharter`, `dygraphs`, `igraph`, `visNetwork`, `networkD3`</font>
       
<br/>

- <font size="+3">Some notes</font>
    - <font size="+2">The demo introduces some libraries that could be useful in visualization. In particular</font>
        - `highcharter`: used for multiple purposes, such as scatter, histogram, graph, map, etc.
        - `dygraphs`: used for time series.
        - `igraph`, `visNetwork`, `networkD3`: used for networks.
    - <font size="+2">Most examples in this demo are from documents/tutorials of each library</font>
    - <font size="+2">In general, this demo could be used as a template. After modification (layouts, data, etc) based on requirement, re-run the source file `demo.Rmd` (`Knit to flex_dashboard` in RStudio).</font>
    - <font size="+2">For more inforamtion, please check [References](#references).</font>



knitr {data-navmenu='Table'}
======================================================================= 


Column
-----------------------------------------------------------------------

### **knitr::kable**
```{r}
kable(iris, row.names = TRUE)
```



DT {data-navmenu='Table'}
======================================================================= 


Column 
-----------------------------------------------------------------------

### **DT::datatable** 
```{r}
datatable(iris, filter = 'top')
```



highcharter {data-navmenu='Plot'}
======================================================================= 


Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### **Scatter**
```{r}
data(diamonds, economics_long, mpg, package = "ggplot2")

hchart(mpg, "scatter", hcaes(x = displ, y = hwy, group = class))
```

### **Line** 
```{r}
data(citytemp)

highchart() %>% 
  hc_xAxis(categories = citytemp$month) %>% 
  hc_add_series(name = "Tokyo", data = citytemp$tokyo) %>% 
  hc_add_series(name = "London", data = citytemp$london) %>% 
  hc_add_series(name = "Other city", data = (citytemp$tokyo + citytemp$london)/2)
```

### **Histogram**
```{r}
hchart(diamonds$price, name = 'You can zoom in') 
```


### **Density**
```{r}
hchart(density(diamonds$price), type = "area", color = "#B71C1C", name = "Price")
```


### **Graph**
```{r}
N <- 40
net <- sample_gnp(N, p = 2/N)
wc <- cluster_walktrap(net)

V(net)$label <- seq(N)
V(net)$name <- paste("Node ", seq(N))
V(net)$page_rank <- round(page.rank(net)$vector, 2)
V(net)$betweenness <- round(betweenness(net), 2)
V(net)$degree <- degree(net)
V(net)$size <- V(net)$degree
V(net)$comm <- membership(wc)
V(net)$color <- colorize(membership(wc))

hchart(net, layout = layout_with_fr)
```


### **Stock**
```{r}
SPY <- getSymbols("SPY", from = Sys.Date() - lubridate::years(1), auto.assign = FALSE)
SPY <- adjustOHLC(SPY)
SPY.SMA.10 <- SMA(Cl(SPY), n = 5)
SPY.SMA.200 <- SMA(Cl(SPY), n = 100)
SPY.RSI.14 <- RSI(Cl(SPY))
SPY.RSI.SellLevel <- xts(rep(70, NROW(SPY)), index(SPY))
SPY.RSI.BuyLevel <- xts(rep(30, NROW(SPY)), index(SPY))

highchart(type = "stock") %>% 
  # create axis
  hc_yAxis_multiples(create_yaxis(3, height = c(2, 1, 1), turnopposite = TRUE)) %>% 
  # series
  hc_add_series(SPY, yAxis = 0, name = "SPY") %>% 
  hc_add_series(SPY.SMA.10, yAxis = 0, name = "Fast MA") %>% 
  hc_add_series(SPY.SMA.200, yAxis = 0, name = "Slow MA") %>% 
  hc_add_series(SPY$SPY.Volume, color = "gray", yAxis = 1, type = "column",
                name = "Volume") %>% 
  hc_add_series(SPY.RSI.14, yAxis = 2, color = hex_to_rgba("green", 0.7),
                name = "Osciallator") %>%
  hc_add_series(SPY.RSI.SellLevel, color = hex_to_rgba("red", 0.7),
                yAxis = 2, name = "Sell level") %>% 
  hc_add_series(SPY.RSI.BuyLevel, color = hex_to_rgba("blue", 0.7),
                yAxis = 2, name = "Buy level") 
```


### **Map**
```{r}
mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
set.seed(1234)
data_fake <- mapdata %>% 
  select(code = `hc-a2`) %>% 
  mutate(value = 1e5 * abs(rt(nrow(.), df = 10)))

hcmap("countries/us/us-all", data = data_fake, value = "value",
      joinBy = c("hc-a2", "code"), name = "Fake data",
      dataLabels = list(enabled = TRUE, format = '{point.name}'),
      borderColor = "#FAFAFA", borderWidth = 0.1,
      tooltip = list(valueDecimals = 2, valuePrefix = "$", valueSuffix = " USD")) 
```


### **Custom** 
```{r}
colors <- c("#FB1108", "#FD150B", "#FA7806", "#FBE426", "#FCFB8F", "#F3F5E7", "#C7E4EA","#ABD6E6","#9AD2E1")

stars$color <- colorize(log(stars$temp), colors)

x <- c("Luminosity", "Temperature", "Distance")
y <- sprintf("{point.%s:.2f}", c("lum", "temp", "distance"))
tltip <- tooltip_table(x, y)

hchart(stars, "scatter", hcaes(temp, lum, size = radiussun, color = color)) %>% 
  hc_chart(backgroundColor = "black") %>% 
  hc_xAxis(type = "logarithmic", reversed = TRUE) %>% 
  hc_yAxis(type = "logarithmic", gridLineWidth = 0) %>% 
  hc_title(text = "Our nearest Stars") %>% 
  hc_subtitle(text = "In a Hertzsprung-Russell diagram") %>% 
  hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip) %>% 
  hc_size(height = 600)
```



dygraphs {data-navmenu='Plot'}
======================================================================= 


Column 
-----------------------------------------------------------------------

### **Time Series** 
```{r}
lungDeaths <- cbind(mdeaths, fdeaths)

dygraph(lungDeaths) %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 20)
```



visNetwork {data-navmenu='Plot'}
======================================================================= 


Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### **Image** 
```{r}
path_to_images <- "https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/img/indonesia/"
 
nodes <- data.frame(id = 1:4, 
                    shape = c("image", "circularImage"),
                    image = paste0(path_to_images, 1:4, ".png"),
                    label = "I'm an image")
  
edges <- data.frame(from = c(2,4,3,3), to = c(1,2,4,2))

visNetwork(nodes, edges, width = "100%") %>% 
  visNodes(shapeProperties = list(useBorderWithImage = TRUE)) %>%
  visLayout(randomSeed = 2)
```

### **Icon** 
```{r}
nb <- 10
nodes <- data.frame(id = 1:nb, label = paste("Label", 1:nb),
 group = sample(LETTERS[1:3], nb, replace = TRUE), value = 1:nb,
 title = paste0("<p>", 1:nb,"<br>Tooltip !</p>"), stringsAsFactors = FALSE)

edges <- data.frame(from = c(8,2,7,6,1,8,9,4,6,2),
 to = c(3,7,2,7,9,1,5,3,2,9),
 value = rnorm(nb, 10), label = paste("Edge", 1:nb),
 title = paste0("<p>", 1:nb,"<br>Edge Tooltip !</p>"))

visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visGroups(groupname = "A", shape = "icon", 
            icon = list(code = "f0c0", size = 75)) %>%
  visGroups(groupname = "B", shape = "icon", 
            icon = list(code = "f007", color = "red")) %>%
  visGroups(groupname = "C", shape = "icon", 
            icon = list(code = "f1b9", color = "black")) %>%
  visOptions(highlightNearest = list(enabled =TRUE, degree = 2, hover = T)) %>%
  addFontAwesome() %>%
  visLayout(randomSeed = 123)
```

### **Custom** 
```{r}
nodes <- fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/nodes_miserables.json")

edges <- fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/edges_miserables.json")

visNetwork(nodes, edges, height = "700px", width = "100%") %>%
  visOptions(selectedBy = "group", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visPhysics(stabilization = FALSE)
```



networkD3 {data-navmenu='Plot'}
======================================================================= 

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------


### **simpleNetwork** 
```{r}
src <- c("A", "A", "A", "A", "B", "B", "C", "C", "D")
target <- c("B", "C", "D", "J", "E", "F", "G", "H", "I")
networkData <- data.frame(src, target)

simpleNetwork(networkData)
```

### **sankeyNetwork** 
```{r}
URL <- paste0("https://cdn.rawgit.com/christophergandrud/networkD3/", "master/JSONdata/energy.json")
Energy <- fromJSON(URL)

sankeyNetwork(Links = Energy$links, Nodes = Energy$nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             units = "TWh", fontSize = 12, nodeWidth = 30)
```



References
======================================================================= 


<br/>    
<br/>     
<br/>

- <font size="+3">For more information, please check the following resources</font>
    - <font size="+2">[R Markdown](https://rmarkdown.rstudio.com/)</font>
    - <font size="+2">[flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/index.html)</font>
    - <font size="+2">Table</font>
        - [`knitr`](https://github.com/yihui/knitr)
        - [`DT`](https://rstudio.github.io/DT/)
    - <font size="+2">Plot</font>
        - [`highcharter`](http://jkunst.com/highcharter/)
        - [`dygraphs`](https://rstudio.github.io/dygraphs/)
        - [`visNetwork`](https://datastorm-open.github.io/visNetwork/)
        - [`networkD3`](https://christophergandrud.github.io/networkD3/)
       
<br/>








